Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
Idea

>>>>

\pedronis{XXX radical idea, given that there may be no space to discuss the subtle points and that this is really about showing that we can enable such mechanisms and there is already literature that shows that/how they work, to just consider the benchmarks with no maps and no versions and with both?}
